---
title: "Resistance Mapping"
author: "River Watson"
date: '2022-10-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(rgdal)          
library(RColorBrewer) 
library(rasterVis)    
library(ggplot2)      
library(colorspace)
library(dplyr)
library(tidyr)
library(readr)
library(sf)
library(gdistance)
library(riverdist)
library(gstat)
library(sp)
library(scales)
library(magrittr)
library(automap)
library(ResistanceGA)
library(FedData)
library(tidyverse)
library(terra)
library(ecodist)
library(Matrix)
#rm(list = ls())
```

```{r rasters}
p_new<-"+proj=utm +zone=17 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
nlcdClip<- raster("All_Rasters/nlcd_2019_land_cover_Clip.tif")
nlcdClip
nlcdClip<-projectRaster(nlcdClip,crs = p_new, method = "ngb")
nlcdClip
#writeRaster(nlcdClip, "UTMRasters/nlcdclip.tif", format="GTiff", overwrite=TRUE)
plot(nlcdClip)

Cond<- raster("All_Rasters/RawCond_Masked.tif")
Cond<-projectRaster(Cond,crs = p_new, method = "ngb")
#writeRaster(Cond, "UTMRasters/Cond.tif", format="GTiff", overwrite=TRUE)
plot(Cond)

Culv<- raster("All_Rasters/CulvUTM.tif")
Culv<-projectRaster(Culv,crs = p_new, method = "ngb")
#writeRaster(Culv, "UTMRasters/Culv.tif", format="GTiff", overwrite=TRUE)
plot(Culv)

Flowline<- raster("All_Rasters/FlowlineRaster.tif")
Flowline<-projectRaster(Flowline,crs = p_new, method = "ngb")
#writeRaster(Flowline, "UTMRasters/Flowline.tif", format="GTiff", overwrite=TRUE)
plot(Flowline)

StreamSize<- raster("All_Rasters/fac_Clip.tif")
StreamSize<-projectRaster(StreamSize,crs = p_new, method = "ngb")
#writeRaster(StreamSize, "UTMRasters/StreamSizefac.tif", format="GTiff", overwrite=TRUE)
plot(StreamSize)

FlowDirection<- raster("All_Rasters/fdr_Clip.tif")
FlowDirection<-projectRaster(FlowDirection,crs = p_new, method = "ngb")
#writeRaster(FlowDirection, "UTMRasters/FlowDirection.tif", format="GTiff", overwrite=TRUE)
plot(FlowDirection)

Slope<-raster("RGAfiles/Slope_Mask2_Clip.tif")
crs(Slope)
#Slope<-projectRaster(Slope,crs = p_new, method = "ngb")
#writeRaster(Slope, "UTMRasters/Slope.tif", format="GTiff", overwrite=TRUE)
plot(Slope)

Elev<-raster("RGAfiles/Elev_Mask2_Clip.tif")
crs(Elev)
#Elev<-projectRaster(Elev,crs = p_new, method = "ngb")
#writeRaster(Elev, "UTMRasters/Elev.tif", format="GTiff", overwrite=TRUE)
plot(Elev)

RawNLCD<-raster("All_Rasters/RawNLCD_Masked.tif")
plot(RawNLCD)
m3 <-c(0,25,25,25,50,50,50,89,75,90,100,100)
rclmatrix3<- matrix(m3, ncol = 3, byrow = TRUE)
NLCD2<-reclassify(RawNLCD, rcl = rclmatrix3)
NLCD<-raster::crop(NLCD2,Cond)
plot(NLCD2)
RawAOP<-raster("All_Rasters/AOPScaledFix_Clip.tif")
ScalesElev<-raster("All_Rasters/Elev_Rescaled_Conduct.tif")
ScaledSS<-raster("All_Rasters/SS_Rescaled_Conduct.tif")
ScaledSlope<-raster("All_Rasters/Slope_Rescaled_Conduct.tif")
ScaledCond<-raster("All_Rasters/Cond_Rescaled_Conduct.tif")
m3 <-c(-1,1,1)
rclmatrix3<- matrix(m3, ncol = 3, byrow = TRUE)
ScaledCond<-reclassify(ScaledCond, rcl = rclmatrix3)
plot(ScaledCond)
InvSS<-raster("SS.asc")
plot(InvSS)
Cond25<-raster("Cond25.tif")
plot(Cond25)
```

data = read.csv("CulvertsSARPRating.csv")
cord.dec = SpatialPoints(cbind(data$Long, -data$Lat), proj4string = CRS("+proj=longlat"))

plot(cord.dec)
# Setting existing coordinate as lat-long system
cord.dec = SpatialPoints(cbind(data$long, -data$lat), proj4string = CRS("+proj=longlat"))

# Transforming coordinate to UTM using EPSG=26917 for WGS=84, UTM Zone=17N,

cord.UTM <- spTransform(cord.dec, CRS("+init=epsg:26917"))
plot(cord.UTM$coords-10)

```{r stream 30m buffer}
p_new<-"+proj=utm +zone=17 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
Flowlineshp<-st_read("All_Rasters/NHDFlowline_SF.shp")
Flowlineshp <- st_transform(Flowlineshp, crs=p_new)
Flowlineshp<-st_zm(Flowlineshp)
streams_buff <- st_buffer(Flowlineshp, dist = 60)
ggplot() +
  geom_sf(data = streams_buff, color = "blue")
streams_buff <- st_union(streams_buff)
streams_buff <- st_sf(streams_buff)
polygonrst<-raster("All_Rasters/SFBoundingBox.tif")
polygon<-st_read("All_Rasters/SFBoundingBox.shp")
polygon <- st_transform(polygon, crs=p_new)
sf_use_s2(FALSE)
streams_buff <- st_intersection(streams_buff, polygon)
streams_buff <- mask(polygonrst, streams_buff)
plot(streams_buff)
#writeRaster(streams_buff, "UTMRasters/FlowlineBuffer.tif", format="GTiff", overwrite=TRUE)
```


```{r reclass NLCD}
#reclassify data to forested or not
m2 <-c(10,40,0,44,96,0,40,43,100) #from 1 to 40 is zero, from 41 to 43 is one (forested), from 44 to 95 is zero
#cuts out everything except forested 41 42 and 43
rclmatrix2<- matrix(m2, ncol=3, byrow = TRUE)
nlcdreclass<-reclassify(nlcdClip, rclmatrix2)
plot(nlcdreclass)
nlcdClip
nlcdreclass
#writeRaster(nlcdfocal, "UTMRasters/nlcdfocal.tif", format="GTiff", overwrite=TRUE)
#focal analysis-moving window analysisto find percent forest cover
nlcdfocal<- focal(nlcdreclass,fun = function(x){sum(x)/9}, w = matrix(1,3,3))
plot(nlcdfocal)
#writeRaster(nlcdfocal, "UTMRasters/nlcdfocal.tif", format="GTiff", overwrite=TRUE)

#second moving window analysis looking at more cells surrounding the stream cells- this helps, but not enough to be a solution
nlcdfocal25<- focal(nlcdreclass,fun = function(x){sum(x)/25}, w = matrix(1,5,5))
plot(nlcdfocal25)
?focal
#writeRaster(nlcdfocal25, "UTMRasters/nlcdfocal25.tif", format="GTiff", overwrite=TRUE)
```


```{r reclassify everything else, put in UTMs}
p_new<-"+proj=utm +zone=17 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
Culv<-raster("CulvertsSARPRatingUTM2_Point81.tif")
##Culvert Ratings
Culv
Culvfocal<- focal(Culv,w = matrix(1,3,3),fun = max,na.rm=TRUE)
plot(Culvfocal)
Culvfocal
writeRaster(Culvfocal, "Culvfocal3.tif", format="GTiff", overwrite=TRUE)
CuFc<-raster("All_Rasters/Culvfocal3.tif")
CuFc
plot(CuFc)
m3 <-c(NA,NA,100,0,1,90,1,2,66,2,3,33,3,4,1,4,5,100) #1 is mod 2 is minor 3 is severe 4 is insig
rclmatrix3<- matrix(m3, ncol = 3, byrow = TRUE)
culvreclass<-reclassify(CuFc, rcl = rclmatrix3)
plot(culvreclass)
culvreclass
writeRaster(culvreclass, "AOP3reclass100s.tif", format="GTiff", overwrite=TRUE)



##Conductivity Points-not krigged
Cond
Condfocal<- focal(Cond,w = matrix(1,5,5),fun = max, na.rm=TRUE)
plot(Condfocal)
#writeRaster(Condfocal, "Condfocal25.tif", format="GTiff", overwrite=TRUE)
CF<-raster("Condfocal25.tif")
CF
m4 <-c(NA,NA,100,37,260,100,260,450,25,450,686,1) 
rclmatrix4<- matrix(m4, ncol = 3, byrow = TRUE)
condreclass<-reclassify(CF, rcl = rclmatrix4)
plot(condreclass)
condreclass
#writeRaster(condreclass, "cond25reclass100s.tif", format="GTiff", overwrite=TRUE)

##Stream Size- reclass based on natural jenks breaks in arcmap
plot(StreamSize)
StreamSize<-projectRaster(StreamSize,crs = p_new)
SSfocal<- focal(StreamSize,w = matrix(1,9,9),fun = max)
plot(SSfocal)
#writeRaster(SSfocal, "UTMRasters/SSfocal.tif", format="GTiff", overwrite=TRUE)
SSfocal<-raster("UTMRasters/SSfocal.tif")
SSfocal
m5 <-c(-Inf,110750,100,110750,300000,75,300000,563145,50,563145,1878352,1) 
rclmatrix5<- matrix(m5, ncol = 3, byrow = TRUE)
StreamSizereclass<-reclassify(SSfocal,rcl=rclmatrix5)
plot(StreamSizereclass)
#values(StreamSizereclass)[values(StreamSizereclass) < 1] = NA
StreamSizereclass
#writeRaster(StreamSizereclass, "UTMRasters/StreamSizereclass100s.tif", format="GTiff", overwrite=TRUE)

#Slope
Slope
m7 <-c(-1,24,100,24,53,85) 
rclmatrix7<- matrix(m7, ncol = 3, byrow = TRUE)
Slopereclass<-reclassify(Slope, rcl = rclmatrix7)
plot(Slopereclass)
Slopereclass
#raster::writeRaster(Slopereclass, "UTMRasters/Slopereclass.tif", format="GTiff", overwrite=TRUE)

#Elevation
Elev
#m8 <-c(21061,35845,100,35845,62489,85) 
m8 <-c(21060,25000,100,25000,49035,80) 
rclmatrix8<- matrix(m8, ncol = 3, byrow = TRUE)
Elevreclass<-reclassify(Elev, rcl = rclmatrix8)
plot(Elevreclass)
Elevreclass
#raster::writeRaster(Elevreclass, "UTMRasters/Elevreclass.tif", format="GTiff", overwrite=TRUE)


#NLCD
nlcdfocal25
m8 <-c(-1,50,60,50,80,80,80,100,100) 
rclmatrix8<- matrix(m8, ncol = 3, byrow = TRUE)
NLCDreclass<-reclassify(nlcdfocal25, rcl = rclmatrix8)
plot(NLCDreclass)
NLCDreclass
#raster::writeRaster(NLCDreclass, "UTMRasters/NLCDreclass.tif", format="GTiff", overwrite=TRUE)


#getting rid of zeros in rasters
Cu<-raster("RawAOP_Masked.tif")
plot(Cu)
m3<-c(99,101,1)
rclmatrix3<- matrix(m3, ncol = 3, byrow = TRUE)
culvreclass<-reclassify(Cu, rcl = rclmatrix3)
plot(culvreclass)
culvreclass
writeRaster(culvreclass, "RawAOP_Masked0to1.tif", format="GTiff", overwrite=TRUE)
```


```{r distance}
library(riverdist)
#getting nhd through R https://ryanpeek.org/2017-11-05-mapping-with-sf-part-2/
#possible tutorial https://ryanpeek.org/2017-11-21-mapping-with-sf-part-3/

#used these three:
#demo https://github.com/FloodHydrology/riverdist_demo
#https://github.com/mbtyers/riverdist
#https://cran.r-project.org/web/packages/riverdist/vignettes/riverdist_vignette.html
p <- '+proj=longlat +datum=WGS84 +no_defs'
sitepoints <- read.csv("Sites_noLD.csv") %>% 
  st_as_sf(coords = c("Long", "Lat"), crs= p )
SF<- st_read("All_Rasters/SFDissolve.shp")
#Create a temp folder to write network folder too
temp_file<-tempdir()
dir.create(temp_file)
#reproj to UTMs
p_new<-"+proj=utm ep+zone=17 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
SF<-st_transform(SF, crs=p_new)
sitepoints<-st_transform(sitepoints, crs=p_new)
#prep stream data
SF <- SF %>% 
  #remove z information (to make it a 'linear' feature)
  st_zm() %>% 
  #Add ID data
  mutate(
    uid = seq(1, nrow(.)),
    type = 'river'
  )
#export streams to temp file
st_write(SF, paste0(temp_file,"\\SF.shp"), delete_dsn = T)

#Create flownet
flow_net <- line2network(path=temp_file, layer="SF", tolerance = 1)

#save flow network 
save(flow_net, file = paste0(temp_file, "\\riv.rda"))

#prep sites data
pnts<-sitepoints %>% 
  #Define coordinates
  mutate(
    x = st_coordinates(.)[,1],
    y = st_coordinates(.)[,2],
  ) %>% 
  #Add site name
  mutate(site_name = 'Site') %>% 
  st_drop_geometry()

#Snap points to flow network
snap<-xy2segvert(x=pnts$x, y=pnts$y, rivers=flow_net)

#Estimate distances ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#Define river distance between points!
output<-riverdistancemat(
  seg = snap$seg, 
  vert = snap$vert, 
  rivers = flow_net)
library(MASS)
#as.data.frame(output)
#write.csv(output, file = "riverdist.csv")
```


```{r trying gdistance}
#load in mask files of resistance layers
#Culv<-raster("RGAfiles/Culv_Mask2_Clip.tif")
#plot(Culv)
#Culv
Cond<-raster("RGAfiles/Cond_Mask2_Clip.tif")
plot(Cond)
Cond
StreamSize<-raster("RGAfiles/SS_Mask2_Clip.tif")
plot(StreamSize)
StreamSize
#NLCD<-raster("RGAfiles/NLCD_Mask2_Clip.tif")
#plot(NLCD)
#NLCD
Slope<-raster("UTMRasters/Slopereclass.tif")
plot(Slope)
Slope
Elev<-raster("UTMRasters/Elevreclass.tif")
plot(Elev)
Elev
#load in points matched up to each mask
samples<-read_csv("RGAfiles/SitesUTM_noLD.csv")
samples<-SpatialPoints(samples[,c(2,3)])
samples
#make transition objects which is what gdistance uses

Condt<- transition(Cond, transitionFunction=mean, directions=8)
StreamSizet<- transition(StreamSize, transitionFunction=mean, directions=8)
NLCDt<- transition(NLCD, transitionFunction=mean, directions=8)
Slopet<- transition(Slope, transitionFunction=mean, directions=8)
Elevt<- transition(Elev, transitionFunction=mean, directions=8)

RawNLCDt<-transition(RawNLCD, transitionFunction=mean, directions=8)
RawAOPt<-transition(RawAOP, transitionFunction=mean, directions=8)
ScaledSlopet<-transition(ScaledSlope, transitionFunction=mean, directions=8)
ScaledSSt<-transition(ScaledSS, transitionFunction=mean, directions=8)
ScaledElevt<-transition(ScalesElev, transitionFunction=mean, directions=8)
ScaledCondt<-transition(ScaledCond, transitionFunction=mean, directions=8)
NLCD2t<-transition(NLCD2, transitionFunction=mean, directions=8)
InvSSt<-transition(InvSS, transitionFunction=mean, directions=8)
Cond25t<-transition(Cond25, transitionFunction=mean, directions=8)
#run commute distance

CondDistance<-commuteDistance(Condt,samples)
SSDistance<-commuteDistance(StreamSizet,samples)
NLCDDistance<-commuteDistance(NLCDt,samples)
SlopeDistance<-commuteDistance(Slopet,samples)
ElevDistance<-commuteDistance(Elevt,samples)

RawNLCDDistance<-commuteDistance(RawNLCDt,samples)
RawAOPDistance<-commuteDistance(RawAOPt,samples)
ScaledSlopeDistance<-commuteDistance(ScaledSlopet,samples)
ScaledSSDistance<-commuteDistance(ScaledSSt,samples)
ScaledElevDistance<-commuteDistance(ScaledElevt,samples)
ScaledCondDistance<-commuteDistance(ScaledCondt,samples)
NLCD2Distance<-commuteDistance(NLCD2t,samples)
InvSSDistance<-commuteDistance(InvSSt,samples)
Cond25Distance<-commuteDistance(Cond25t,samples)

#export outputs
#CulvDistancec<-as.matrix(CulvDistance)
#CulvDistancec<-as.data.frame(CulvDistancec)
#write.csv(CulvDistancec, file = "CulvDistance.csv")

#CondDistancec<-as.matrix(CondDistance)
#CondDistancec<-as.data.frame(CondDistancec)
#write.csv(CondDistancec, file = "CondDistance.csv")

#SSDistancec<-as.matrix(SSDistance)
#SSDistancec<-as.data.frame(SSDistancec)
#write.csv(SSDistancec, file = "SSDistance.csv")

#NLCDDistancec<-as.matrix(NLCDDistance)
#NLCDDistancec<-as.data.frame(NLCDDistancec)
#write.csv(NLCDDistancec, file = "NLCDDistance.csv")

#SlopeDistancec<-as.matrix(SlopeDistance)
#SlopeDistancec<-as.data.frame(SlopeDistancec)
#write.csv(SlopeDistancec, file = "SlopeDistance.csv")

#ElevDistancec<-as.matrix(ElevDistance)
#ElevDistancec<-as.data.frame(ElevDistancec)
#write.csv(ElevDistancec, file = "ElevDistance.csv")
```

```{r gdistance combined}
#load in mask files of resistance layers
#Culv<-raster("RGAfiles/Culv_Mask2_Clip.tif")
#plot(Culv)
Cond<-raster("RGAfiles/Cond_Mask2_Clip.tif")
plot(Cond)
StreamSize<-raster("RGAfiles/SS_Mask2_Clip.tif")
plot(StreamSize)
#NLCD<-raster("RGAfiles/NLCD_Mask2_Clip.tif")
#plot(NLCD)
Slope<-raster("UTMRasters/Slopereclass.tif")
plot(Slope)
Elev<-raster("UTMRasters/Elevreclass.tif")
plot(Elev)
#make raster brick-cant use raster stack in gdistacne
r.brick <- brick(RawAOP,Cond,NLCD,StreamSize,Slope,Elev)
#read in samples
samples1<-read_csv("RGAfiles/SitesUTM_noLD.csv")
samples<-SpatialPoints(samples1[,c(2,3)])
#make transition object which is what gdistance uses
#error-method mahal isnt working, listed as a bug on guthub
cost<-(RawAOP + Cond + NLCD + StreamSize + Slope + Elev)
cost
plot(cost)
#rbrickt <- transition(r.brick, transitionFunction="mahal", directions=8)
tr.cost1 <- gdistance::transition(cost, transitionFunction=mean, directions=8) 
tr.cost1
par(mar=c(2,2,1,1))
raster::plot(raster::raster(tr.cost1))
#raster::writeRaster(cost, "RGAfiles/CombinedConductanceRaster.tif", format="GTiff", overwrite=TRUE)
tr.cost1 <- gdistance::geoCorrection(tr.cost1,type = "c",multpl=FALSE)

allDistance<-commuteDistance(tr.cost1,samples)
#AllDistancec<-as.matrix(allDistance)
#AllDistancec<-as.data.frame(AllDistancec)
#write.csv(AllDistancec, file = "CombinedDistance.csv")

#least cost paths
lcpDistance <- gdistance::costDistance(tr.cost1,samples)

#compare the two
#dist_df <- data.frame("lcpDistance"=as.numeric(lcpDistance),
 #                     "allDistance"=as.numeric(allDistance))
#correlation  <- cor(dist_df$lcpDistance, dist_df$allDistance, method = "spearman")
#correlation #=0.9992833

#making combos of resistance layers
CuCoNLSS<-(RawAOP + Cond + NLCD + StreamSize)
CuCoNLSS <- gdistance::transition(CuCoNLSS, transitionFunction=mean, directions=8) 
CuCoNLSS <- gdistance::geoCorrection(CuCoNLSS,type = "c",multpl=FALSE)
CuCoNLSSDistance<-commuteDistance(CuCoNLSS,samples)

SlEl<-(Slope + Elev)
SlEl <- gdistance::transition(SlEl, transitionFunction=mean, directions=8) 
SlEl <- gdistance::geoCorrection(SlEl,type = "c",multpl=FALSE)
SlElDistance<-commuteDistance(SlEl,samples)

SlElNL<-(Slope + Elev+NLCD)
SlElNL <- gdistance::transition(SlElNL, transitionFunction=mean, directions=8) 
SlElNL <- gdistance::geoCorrection(SlElNL,type = "c",multpl=FALSE)
SlElNLDistance<-commuteDistance(SlElNL,samples)

CuCo<-(RawAOP + Cond)
CuCo <- gdistance::transition(CuCo, transitionFunction=mean, directions=8) 
CuCo <- gdistance::geoCorrection(CuCo,type = "c",multpl=FALSE)
CuCoDistance<-commuteDistance(CuCo,samples)

CoNL<-(Cond + NLCD2)
plot(CoNL)
CoNL <- gdistance::transition(CoNL, transitionFunction=mean, directions=8) 
CoNL <- gdistance::geoCorrection(CoNL,type = "c",multpl=FALSE)
CoNLDistance<-commuteDistance(CoNL,samples)

CuNL<-(RawAOP + NLCD)
CuNL <- gdistance::transition(CuNL, transitionFunction=mean, directions=8) 
CuNL <- gdistance::geoCorrection(CuNL,type = "c",multpl=FALSE)
CuNLDistance<-commuteDistance(CuNL,samples)

noSS<-(RawAOP + Cond + NLCD + Slope + Elev)
noSS <- gdistance::transition(noSS, transitionFunction=mean, directions=8) 
noSS <- gdistance::geoCorrection(noSS,type = "c",multpl=FALSE)
noSSDistance<-commuteDistance(noSS,samples)
```

```{r pearsons correlation tests}
#read in all the data
library(hierfstat)
library(adegenet)
CulvDistance<-read.csv("CulvDistance.csv")
CulvDistance<-CulvDistance[,2:13]
CulvDistance<-lower(CulvDistance)
CondDistance<-read.csv("CondDistance.csv")
CondDistance<-CondDistance[,2:13]
CondDistance<-lower(CondDistance)
NLCDDistance<-read.csv("NLCDDistance.csv")
NLCDDistance<-NLCDDistance[,2:13]
NLCDDistance<-lower(NLCDDistance)
SSDistance<-read.csv("SSDistance.csv")
SSDistance<-SSDistance[,2:13]
SSDistance<-lower(SSDistance)
SlopeDistance<-read.csv("SlopeDistance.csv")
SlopeDistance<-SlopeDistance[,2:13]
SlopeDistance<-lower(SlopeDistance)
ElevDistance<-read.csv("ElevDistance.csv")
ElevDistance<-ElevDistance[,2:13]
ElevDistance<-lower(ElevDistance)
#mlpe with all resitance distances
allDistance<-lower(allDistance)
Data <- read.genepop("KAD_Watson_GenepopFile_12popNo519.gen") 
Datahier <- genind2hierfstat(Data)
wcpw <-pairwise.WCfst(Datahier, diploid = TRUE)
wcpw<-lower(wcpw)
output<-read.csv("riverdist.csv")#from riverdist
output<-output[,2:13]
riverdist<-lower(output)
riverdist

#riverdistances are currently in unlogtransformed meters instead of logtransformed km
library(measurements)
as.data.frame(output)
outputkm <- measurements::conv_unit(output,"m","km")
logkmrd<-log(outputkm)
distlg<-as.matrix(logkmrd)
distlg<-lower(outputkm)
output<-as.matrix(output)
output<-lower(output)
cor.test(allDistance,riverdist)
#positive correlation 0.3620896, p-value = 0.002813

cor.test(SS_jlResistMatCopy,output)
#	Pearson's product-moment correlation
#data:  SS_jlResistMatCopy and output
#t = 47.519, df = 142, p-value < 2.2e-16
#alternative hypothesis: true correlation is not equal to 0
#95 percent confidence interval:
# 0.9584640 0.9783195
#sample estimates:
#      cor 
#0.9699669 
```


```{r putting gdistance results into mlpe model from RGA}
#run wc fst-make a vector
library(hierfstat)
library(adegenet)
Data <- read.genepop("KAD_Watson_GenepopFile_12popNo519.gen")
Datahier <- genind2hierfstat(Data)
wcpw <-pairwise.WCfst(Datahier, diploid = TRUE)
fst<-lower(wcpw)
#log river distance
output<-read.csv("riverdist.csv")#from riverdist
output<-output[,2:13]
riverdist<-lower(output)
riverdist
#combined resistance distance
allDistance
allDistance<-as.vector(allDistance)
all<-MLPE.lmm(allDistance,fst)
#Culv, Cond, NLCD, SS

#run mple model from resistanceGA
#This function will run the model and return lmer object
#all 6 resistance layers
dist<-MLPE.lmm(output,fst)
summary(dist)
library(MuMIn)
r.squaredGLMM(dist)


allDistance
library(lme4)
library(AICcmodavg)
mods<-list(all,dist)
aictab(mods)
#now try 4, no slope or elevation
four<-MLPE.lmm(CuCoNLSSDistance,fst)
#just slope and elevation
SE<-MLPE.lmm(SlElDistance,fst)
#just culverts and conductivity
CC<-MLPE.lmm(CuCoDistance,fst)
#Cond and NLCD
CoN<-MLPE.lmm(CoNLDistance,fst)
#all minus SS
NoSS<-MLPE.lmm(noSSDistance,fst)
#Culv + NLCD
CuNL<-MLPE.lmm(CuNLDistance,fst)
#Slope + Elev + NLCD
SlElNL<-MLPE.lmm(SlElNLDistance,fst)
#all individually
mCond<-MLPE.lmm(CondDistance,fst)
summary(mCond)
mNLCD<-MLPE.lmm(NLCDDistance,fst)
summary(mNLCD)
mSS<-MLPE.lmm(SSDistance,fst)
summary(mSS)
mSlope<-MLPE.lmm(SlopeDistance,fst)
summary(mSlope)
mElev<-MLPE.lmm(ElevDistance,fst)

mRawNLCD<-MLPE.lmm(RawNLCDDistance,fst)
mRawAOP<-MLPE.lmm(RawAOPDistance,fst)
mScaledSlope<-MLPE.lmm(ScaledSlopeDistance,fst)
mScaledElev<-MLPE.lmm(ScaledElevDistance,fst)
mScaledSS<-MLPE.lmm(ScaledSSDistance,fst)
mScaledCond<-MLPE.lmm(ScaledCondDistance,fst)
mNLCD2<-MLPE.lmm(NLCD2Distance,fst)
mInvSS<-MLPE.lmm(InvSSDistance,fst)
mCond25<-MLPE.lmm(Cond25Distance,fst)


library(AICcmodavg)
model.list<-list(all,dist,mCond,mNLCD,mSS,mSlope,mElev,four,SE,CC,CoN,NoSS,CuNL,SlElNL,mRawNLCD,mRawAOP,mScaledSlope,mScaledElev,mScaledSS,mScaledCond,mNLCD2,mInvSS,mCond25)
names<-c("all","dist","mCond","mNLCD","mSS","mSlope","mElev","four","SE","CC","CoN","NoSS","CuNL","SlElNL","mRawNLCD","mRawAOP","mScaledSlope","mScaledElev","mScaledSS","mScaledCond","mNLCD2","InvSS","mCond25")
table<-aictab(model.list, modnames = names)

plot(Cond25Distance,fst)
r.squaredGLMM(SlElNL)

#ls()
#save.image(file='myEnvironment2.RData')
#load('myEnvironment.RData')
#write_xlsx(table,"ModelRanks_AIC.xlsx")


#The code below does the EXACT SAME THING as MLPE.lmm, MLPE.lmm just does all of the work for you
# Generate to-from object
#  id <- To.From.ID(nrow(samples1))
#  df1 <- data.frame(fst,
#                  allDistance,
#                   pop = id$pop1)
#  mod1 <- mlpe_rga(formula = fst ~ allDistance + (1 | pop),
#                   data = df1)
#  summary(mod1)
  
#  df2 <- data.frame(fst,
#                  riverdistance,
#                   pop = id$pop1)
#  mod2 <- mlpe_rga(formula = fst ~ riverdist + (1 | pop),
#                   data = df2)
#  summary(mod2)
# AIC(mod1, mod2)
```

```{r all model combinations (36)}
m1<-(RawAOP)
m1 <- gdistance::transition(m1, transitionFunction=mean, directions=8)
m1<-commuteDistance(m1,samples)
m1<-MLPE.lmm(m1,fst)

m2<-(RawAOP + Cond)
m2 <- gdistance::transition(m2, transitionFunction=mean, directions=8)
m2<-commuteDistance(m2,samples)
m2<-MLPE.lmm(m2,fst)

m3<-(RawAOP + Cond + NLCD)
m3 <- gdistance::transition(m3, transitionFunction=mean, directions=8)
m3<-commuteDistance(m3,samples)
m3<-MLPE.lmm(m3,fst)

m4<-(RawAOP + Cond + NLCD + StreamSize)
m4 <- gdistance::transition(m4, transitionFunction=mean, directions=8)
m4<-commuteDistance(m4,samples)
m4<-MLPE.lmm(m4,fst)

m5<-(RawAOP + Cond + NLCD + StreamSize + Slope)
m5 <- gdistance::transition(m5, transitionFunction=mean, directions=8)
m5<-commuteDistance(m5,samples)
m5<-MLPE.lmm(m5,fst)

m6<-(RawAOP + Cond + NLCD + StreamSize + Slope + Elev)
m6 <- gdistance::transition(m6, transitionFunction=mean, directions=8)
m6<-commuteDistance(m6,samples)
m6<-MLPE.lmm(m6,fst)

m7<-(Cond)
m7 <- gdistance::transition(m7, transitionFunction=mean, directions=8)
m7<-commuteDistance(m7,samples)
m7<-MLPE.lmm(m7,fst)

m8<-(NLCD + Cond)
m8 <- gdistance::transition(m8, transitionFunction=mean, directions=8)
m8<-commuteDistance(m8,samples)
m8<-MLPE.lmm(m8,fst)

m9<-(RawAOP + Cond + Slope)
m9 <- gdistance::transition(m9, transitionFunction=mean, directions=8)
m9<-commuteDistance(m9,samples)
m9<-MLPE.lmm(m9,fst)

m10<-(RawAOP + Cond + NLCD + Slope)
m10 <- gdistance::transition(m10, transitionFunction=mean, directions=8)
m10<-commuteDistance(m10,samples)
m10<-MLPE.lmm(m10,fst)

m11<-(RawAOP + Cond + NLCD + Elev + Slope)
m11 <- gdistance::transition(m11, transitionFunction=mean, directions=8)
m11<-commuteDistance(m11,samples)
m11<-MLPE.lmm(m11,fst)

m12<-(NLCD)
m12 <- gdistance::transition(m12, transitionFunction=mean, directions=8)
m12<-commuteDistance(m12,samples)
m12<-MLPE.lmm(m12,fst)

m13<-(NLCD + RawAOP)
m13 <- gdistance::transition(m13, transitionFunction=mean, directions=8)
m13<-commuteDistance(m13,samples)
m13<-MLPE.lmm(m13,fst)

m14<-(NLCD + Cond + Slope)
m14 <- gdistance::transition(m14, transitionFunction=mean, directions=8)
m14<-commuteDistance(m14,samples)
m14<-MLPE.lmm(m14,fst)

m15<-(NLCD + Cond + Elev + Slope)
m15 <- gdistance::transition(m15, transitionFunction=mean, directions=8)
m15<-commuteDistance(m15,samples)
m15<-MLPE.lmm(m15,fst)

m16<-(RawAOP + Cond + NLCD + Elev + StreamSize)
m16 <- gdistance::transition(m16, transitionFunction=mean, directions=8)
m16<-commuteDistance(m16,samples)
m16<-MLPE.lmm(m16,fst)

m17<-(StreamSize)
m17 <- gdistance::transition(m17, transitionFunction=mean, directions=8)
m17<-commuteDistance(m17,samples)
m17<-MLPE.lmm(m17,fst)

m18<-(StreamSize + RawAOP)
m18 <- gdistance::transition(m18, transitionFunction=mean, directions=8)
m18<-commuteDistance(m18,samples)
m18<-MLPE.lmm(m18,fst)

m19<-(StreamSize + Cond + Slope)
m19 <- gdistance::transition(m19, transitionFunction=mean, directions=8)
m19<-commuteDistance(m19,samples)
m19<-MLPE.lmm(m19,fst)

m20<-(StreamSize + Cond + Elev + Slope)
m20 <- gdistance::transition(m20, transitionFunction=mean, directions=8)
m20<-commuteDistance(m20,samples)
m20<-MLPE.lmm(m20,fst)

m21<-(RawAOP + Cond + NLCD + Slope + StreamSize)
m21 <- gdistance::transition(m21, transitionFunction=mean, directions=8)
m21<-commuteDistance(m21,samples)
m21<-MLPE.lmm(m21,fst)

m25<-(Slope)
m25 <- gdistance::transition(m25, transitionFunction=mean, directions=8)
m25<-commuteDistance(m25,samples)
m25<-MLPE.lmm(m25,fst)

m22<-(Slope + RawAOP)
m22 <- gdistance::transition(m22, transitionFunction=mean, directions=8)
m22<-commuteDistance(m22,samples)
m22<-MLPE.lmm(m22,fst)

m23<-(Slope + Cond + Elev)
m23 <- gdistance::transition(m23, transitionFunction=mean, directions=8)
m23<-commuteDistance(m23,samples)
m23<-MLPE.lmm(m23,fst)

m24<-(Slope + Cond + Elev + RawAOP)
m24 <- gdistance::transition(m24, transitionFunction=mean, directions=8)
m24<-commuteDistance(m24,samples)
m24<-MLPE.lmm(m24,fst)

m26<-(Elev)
m26 <- gdistance::transition(m26, transitionFunction=mean, directions=8)
m26<-commuteDistance(m26,samples)
m26<-MLPE.lmm(m26,fst)

m27<-(Elev + RawAOP)
m27 <- gdistance::transition(m27, transitionFunction=mean, directions=8)
m27<-commuteDistance(m27,samples)
m27<-MLPE.lmm(m27,fst)

m28<-(RawAOP + Cond + Elev)
m28 <- gdistance::transition(m28, transitionFunction=mean, directions=8)
m28<-commuteDistance(m28,samples)
m28<-MLPE.lmm(m28,fst)

m29<-(Cond + Elev + RawAOP + NLCD)
m29 <- gdistance::transition(m29, transitionFunction=mean, directions=8)
m29<-commuteDistance(m29,samples)
m29<-MLPE.lmm(m29,fst)

aic<-list(m1,m2,m3,m4,m5,m6,m7,m8,m9,m10,m11,m12,m13,m14,m15,m16,m17,m18,m19,m20,m21,m22,m23,m24,m25,m26,m27,m28,m29)
aictab(aic)
#AIC(all,dist,mCulv,mCond,mNLCD,mSS,mSlope,mElev,four,SE,CC,CoN,NoSS,CuNL,SlElNL,m1,m2,m3,m4,m5,m6,m7,m8,m9,m10,m11,m12,m13,m14,m15,m16,m17,m18,m19,m20,m21,m22,m23,m24,m25,m26,m27,m28,m29)
```



